---
title: "Cabbages"
author: "Issa Darrouj"
date: "Fall 2025"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(MASS)
veggy <- cabbages
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
 The cabbages data from the MASS package is loaded into a dataframe called veggy. Complete this report by answering the following two questions  
 
### Is there a difference in average VitC between c39 and c52 cultivation methods?  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

After looking at the data, I realized that I am working with numerical data (VitC) which was written in integers explained by categorical data (Cult). And so I decided to use the numerical~categorical data to be able to explain VitC (numerical) by Cult (catagorical), and thus I knew which helper file to work with to help me with this assignment.

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(VitC~Cult,data=veggy)
```

This boxplot is showing that the amount of VitC is dependent on the Cult method. What I noticed and found out is that the first quartile of the c52 method is bigger that the third quartile of the c39 method, this means that the c52 is significantly more different than the c39 method.  

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(VitC~Cult,data=veggy)
```

The favstats showed the values of both Cult methods. While looking at them, I saw that the Q1 value of c52 method which is 58 is already larger than the Q3 value of c39 method which is 54.75, showing that c52 methods has more amount of VitC. Normally in this situation the statistical result show that c52 is significantly different than c39. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(VitC~Cult,data=veggy)
```

The chances of getting a result like this is 0.00000003405. And when you get a p-value that is that small, then I can conclude that these two cult methods are significantly different.

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

After comparing both Cult methods using boxplot, favstats, and t-test. I was able to conclude that the VitC content depends on the Cult method. All of the methods supported that. The boxplot and the favstats showed that the Q1 of c52 which was 58 is higher than the Q3 of the c39 method which was 54.75, which showed me that there is a statistical difference between the two cult methods. Moreover, after making a t-test, I saw that the p-value was really small and was 0.00000003405, and when the p-value is that small, then that made me conclude that the two cult methods are significantly different.
